MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-08-12 main/MSstatsPTM_Main.tex
Small

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_fc.png}
\caption{}
\label{fig:spikein_boxplot}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_volcano.png}
\caption{}
\label{fig:spikein_prop_volcano}
\end{subfigure}
\caption{Dataset 3: Spike-in benchmark - Ubiquitination - Label-free. \todo{explain the meaning of vertical solid vs dashed lines; and of the horizontal line} a) Before adjustment the fold change of the spike-in peptides' were systematically different from the expected fold change in all models. After adjustment, this systemic difference was removed, however the inner quartile range of the $Limma$ and $ANOVA$ models was wider than the proposed method. b) Before adjustment the spike-in peptides (colored red) did not follow the expected log fold change; after adjustment, the spike-in peptides were more in line with expectation. Using $Limma$, the spike-in peptides followed the expected log fold change after adjustment, however the majority of spike-in peptides did not have a significant adjusted p-value.}
\label{fig:spikein_volcano}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_fc.png}
\caption{}
\label{fig:spikein_boxplot}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_volcano.png}
\caption{}
\label{fig:spikein_prop_volcano}
\end{subfigure}
\caption{Dataset 3: Spike-in benchmark - Ubiquitination - Label-free. a) Before adjustment the fold change of the spike-in peptides' were systematically different from the expected fold change in all models. After adjustment, this systemic difference was removed, however the inner quartile range of the $Limma$ and $ANOVA$ models was wider than the proposed method. b) \todo{explain the meaning of vertical solid vs dashed lines; and of the horizontal line}  Before adjustment the spike-in peptides (colored red) did not follow the expected log fold change; after adjustment, the spike-in peptides were more in line with expectation. Using $Limma$, the spike-in peptides followed the expected log fold change after adjustment, however the majority of spike-in peptides did not have a significant adjusted p-value.}
\label{fig:spikein_volcano}
\end{figure}
